Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-30 paper/abstract.tex
Remove mention of 2nd case study

Cyber-physical systems, such as avionics, must be tolerant to
cyber-attacks in the same way they are tolerant to random faults: they
should either gracefully recover or safely shut down as requirements dictate.
%
%% The DARPA Cyber Assured Systems Engineering program is developing
%% tools for design, analysis, and verification that enable systems
%% engineers to design-in cyber-resiliency in a Model-Based Systems
%% Engineering (MBSE) environment.
%
This paper describes automated model transformations that introduce
high-assurance cyber-resiliency components into a system; in
particular, filters that guard against malformed input, as well as
monitors that guard against spoofing and other malicious behavior. A
formal specification in the form of a code contract defines each
high-assurance component and is used to verify that the component
addresses system-level cyber requirements. Implementations for these
high-assurance components are directly synthesized from their code
contracts, and are backed up by proofs showing that high-level
specifications map in a menaing-preserving way to code. The model
transformations are integrated into the Open Source AADL Tool
Environment (OSATE).  We further report on two case studies, one by
formal method experts and the other by non-experts, applying model
transformations to two different systems to improve cyber resiliency
using high-assurance filters and monitors.  One is a UAV system
utilizing the Air Force Research Laboratory's OpenUxAS services for
route planning.  The other is a tablet used for situational awareness
in a CH-47F Chinook helicopter application.  The case studies
demonstrate that our MBSE approach is feasible in real-world systems
engineering.

>>>>

Cyber-physical systems, such as avionics, must be tolerant to
cyber-attacks in the same way they are tolerant to random faults: they
should either gracefully recover or safely shut down as requirements dictate.
%
%% The DARPA Cyber Assured Systems Engineering program is developing
%% tools for design, analysis, and verification that enable systems
%% engineers to design-in cyber-resiliency in a Model-Based Systems
%% Engineering (MBSE) environment.
%
This paper describes automated model transformations that introduce
high-assurance cyber-resiliency components into a system; in
particular, filters that guard against malformed input, as well as
monitors that guard against spoofing and other malicious behavior. A
formal specification in the form of a code contract defines each
high-assurance component and is used to verify that the component
addresses system-level cyber requirements. Implementations for these
high-assurance components are directly synthesized from their code
contracts, and are backed up by proofs showing that high-level
specifications map in a meaning-preserving way to code. The model
transformations are integrated into the Open Source AADL Tool
Environment (OSATE). 
We further report a case study applying the model
transformations to a UAV system
utilizing the Air Force Research Laboratory's OpenUxAS services for
route planning.  The case study
demonstrates that our MBSE approach is feasible in real-world systems
engineering.

% We further report on two case studies, one by
% formal method experts and the other by non-experts, applying model
% transformations to two different systems to improve cyber resiliency
% using high-assurance filters and monitors.  One is a UAV system
% utilizing the Air Force Research Laboratory's OpenUxAS services for
% route planning.  The other is a tablet used for situational awareness
% in a CH-47F Chinook helicopter application.  The case studies
% demonstrate that our MBSE approach is feasible in real-world systems
% engineering.
